---
title: "Some Simple Plots"
author: "``r Sys.getenv('USER')``"
date: "``r Sys.Date()``"
output:
  html_document:
    toc: true
    theme: united
    number_sections: true
    highlight: tango
---

# Reproducible Results

## Uninitialised

```{r sample.int.10}
print(sample.int(10))
print(sample.int(10))
```

## Initialised

```{r sample.int.10.init}
set.seed(5)
print(sample.int(10))
set.seed(5)
print(sample.int(10))
```


# Uniform Distribution

```{r runif100}
plot(runif(100,1,99))
```

```{r runif100sorted}
plot(sort(runif(100,1,99)))
```

```{r runif1000sorted}
plot(sort(runif(1000,1,99)))
```

# Sampling

## Without Putting Back

```{r sample100}
plot(sample(100))
```

```{r sample100sorted}
plot(sort(sample(100)))
```

### Random Sampling of a Larger Set

#### For Vectors

```{r sampling.larger.vector}
larger.vect <- rnorm(50)
vect.sample.of.five <- larger.vect[sample(length(larger.vect),5)]
print(larger.vect)
```

The sample: `r vect.sample.of.five`.

#### For Data Sets

```{r sampling.larger.set}
larger.set <- data.frame(rnums = rnorm(50))
vect2.sample.of.five <- larger.set[sample(nrow(larger.set),5),]
print(str(larger.set))
print(head(larger.set))
print(tail(larger.set))
```

The sample: `r vect2.sample.of.five`.

## With Putting Back

```{r sample100.putback}
plot(sample(100,replace=T))
```

```{r sample100sorted.putback}
plot(sort(sample(100,replace=T)))
```

# runif vs sample

`runif` and `sample` produce similar results but they are not identical:

```{r runif.vs.sample}
set.seed(5)
round(runif(10,1,10))
set.seed(5)
print(sample.int(10))
```

```{r sample1000sorted.putback}
plot(sort(sample(1000,replace=T)))
```

```{r runif1000sorted.b}
plot(sort(runif(1000,1,1000)))
```

# Binomial Distribution

```{r rbinom100_0.5}
plot(rbinom(100,10,0.5))
```

```{r rbinom100_0.1}
plot(rbinom(100,10,0.1))
```

```{r rbinom100_0.5_sorted}
plot(sort(rbinom(100,10,0.5)))
```
```{r rbinom100_0.1_sorted}
plot(sort(rbinom(100,10,0.1)))
```

# Normal Distribution

```{r rnorm1000}
plot(rnorm(1000))
```

```{r rnorm1000.sorted}
plot(sort(rnorm(1000)))
```

# Density Distribution

```{r rexp1000}
plot(rexp(1000))
```

```{r rexp1000.sorted}
plot(sort(rexp(1000)),pch=".")
```

# Histograms

```{r hist.rnorm.500.50.10}
hist(rnorm(500,mean=50,sd=10))
```

## Multiple

### Histograms

```{r hist.rnorm.500.50.double}
hist(rnorm(500,mean=50,sd=10),col=rgb(1,0,0,1/4),ylim=c(0,200),breaks=seq(10,90,5))
hist(rnorm(500,mean=50,sd=5),col=rgb(0,0,1,1/4),add=T)
```

### Trend Curve on Histogram

```{r hist.rexp.100.1500th.with.curv}
x=rexp(100, 1/1500)
hist(x, probability=TRUE, col= gray(.9), main="exponential mean=1500")
curve(dexp(x, 1/1500), add= T)
```

# Reference

Main source:

1. [Random Number Generator in R](https://www.educba.com/random-number-generator-in-r/) 
2. [R Markdown: Basic Syntax](https://www.markdownguide.org/basic-syntax)

Plus lots of internet searches.
