---
title: "Introduction to R Markdown 2"
author: "``r Sys.info()[[7]]``"
date: "``r Sys.Date()``"
output:
  html_document:
    toc: true
    number_sections: true

---

```{r, echo=F, message=F, warning=F, error=F, results='hide'}
library(nasaweather)
library(dplyr)
library(ggvis)
```

# Ozone

## Data

The `atmos` data set resides in the `nasaweather` package of the *R* programming language. It contains a collection of atmospheric variables measured between 1995 and 2000 on a grid of 576 coordinates in the western hemisphere. The data set comes from the [2006 ASA Data Expo](http://stat-computing.org/dataexpo/2006/).

Some of the variables in the `atmos` data set are:

* __temp__ - The mean monthly air temperature near the surface of the Earth (measured in degrees kelvin (_K_))
* __pressure__ - The mean monthly air pressure at the surface of the Earth (measured in millibars (_mb_))
* __ozone__ - The mean monthly abundance of atmospheric ozone (measured in Dobson units (_DU_))

You can convert the temperature unit from Kelvin to Celsius with the formula

$$ celsius = kelvin - 273.15 $$

And you can convert the result to Fahrenheit with the formula

$$ fahrenheit = celsius \times \frac{5}{9} + 32 $$

Backwards:

$$ celsius =  (fahrenheit - 32) \times \frac{9}{5} $$

## Reformat Data with dplyr

```{r}
year <- 1995

means <- atmos %>% 
  filter(year == year) %>%
  group_by(long, lat) %>%
  summarize(temp = mean(temp, na.rm = TRUE), 
         pressure = mean(pressure, na.rm = TRUE),
         ozone = mean(ozone, na.rm = TRUE),
         cloudlow = mean(cloudlow, na.rm = TRUE),
         cloudmid = mean(cloudmid, na.rm = TRUE),
         cloudhigh = mean(cloudhigh, na.rm = TRUE)) %>%
  ungroup()

print(means)
```

## Plot pressure vs ozone (ggvis)

```{r}
means %>% 
  ggvis(x = ~pressure, y = ~ozone) %>%
  layer_points()
```

## Plot temp vs ozone (ggvis)

```{r}
means %>% 
  ggvis(x = ~temp, y = ~ozone) %>%
  layer_points()
```

## Model (Linear)

```{r}
mod <- lm(ozone ~ temp, data = means)
summary(mod)
```

