---
title: "Introduction to R Markdown"
author: "``r Sys.info()[[7]]``"
date: "``r Sys.Date()``"
output: html_document
---

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

Using the **rmarkdown** package (`pandoc` version 1.12.3 or higher is required), the rendering command is

```{r, eval=F}
rmarkdown::render("your rmd file")
```

The default is HTML output (because `output` has been specified as such in the heading of the current document). If you would like a markdown (.md) or github (to include graphics, with preview in html) document, add an argument:

```{r, eval=F}
rmarkdown::render("your rmd file", md_document())
rmarkdown::render("your rmd file", github_document())
```

---

The same way, PDF output (`pdflatex` is needed, that is `texlive-base`, `texlive-latex-base`, `texlive-latex-extra`, and `texlive-fonts-recommended`):

```{r, eval=F}
rmarkdown::render("your rmd file", pdf_document())
```

or OpenOffice or Word document:

```{r, eval=F}
rmarkdown::render("your rmd file", odt_document())
rmarkdown::render("your rmd file", word_document())
```

or `beamer` (PDF) or `slidy` (HTML) presentation:

```{r, eval=F}
rmarkdown::render("your rmd file", beamer_presentation())
rmarkdown::render("your rmd file", slidy_presentation())
```

---

When the document is generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(mtcars)
```

---

You can also embed plots, for example:

```{r, echo=FALSE}
plot(mpg~hp, data=mtcars, main="Mileage per Horsepower")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Session Information

```{r}
sessionInfo()
```

## Supported Languages

```{r}
library(knitr)
names(knitr::knit_engines$get())
```

### Some Perl

```{r, engine="perl", eval=F}
package TS v0.0.1 {
    sub ts {
        my @art = localtime(time);
        return sprintf("%4d%02d%02d_%02d%02d%02d",
                       $art[5]+1900, # year
                       ++$art[4],    # month
                       $art[3],      # day
                       $art[2],      # hour
                       $art[1],      # minute
                       $art[0]);     # second
    }
}
1;
```

### Some C

```{r, engine="c", eval=F}
#include <stdio.h>
#include <stdlib.h>
#include <signal.h>
#include <time.h>
#include <unistd.h>
#include <stdbool.h>

time_t start, end;

void signal_callback_handler(int signum)
{
   printf("Caught signal %d\n",signum);
   printf("end: %ld\n",(long)end);
   double time_difference = difftime(end,start);
   printf("%lfs has passed.\n",time_difference);
   exit(signum);
}


int main(int argc, char** argv)
{
  signal(SIGINT, signal_callback_handler);
  bool ticktack = true;
  start = end = time(NULL);
  printf("start: %ld\n",(long)start);
  //long long counter = 0;
  while(1)
    {
      if (ticktack)
	{
	  puts("tick");
	  ticktack = false;
	}
      else
	{
	  puts("tack");
	  ticktack = true;
	}
      sleep(1);
      end = time(NULL);
      //counter++;
    }
  //printf("%lld loop cyles for one clock tick\n",counter);

  return 0;
}

```