---
title: "Introduction to R Markdown"
author: "Tiberius"
date: "9 July 2016"
output: html_document
---

Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

Using the **rmarkdown** package (*pandoc* version 1.12.3 or higher is required), the rendering command is

```{r, eval=F}
rmarkdown::render("your rmd file")
```

The default is HTML output (because *output* has been specified as such in the heading of the current document). If you would like a markdown (.md) document, add an argument:

```{r, eval=F}
rmarkdown::render("your rmd file", md_document())
```

---

The same way, PDF output (*pdflatex* is needed, that is *texlive-base*, *texlive-latex-base*, *texlive-latex-extra*, and *texlive-fonts-recommended*):

```{r, eval=F}
rmarkdown::render("your rmd file", pdf_document())
```

or OpenOffice or Word document:

```{r, eval=F}
rmarkdown::render("your rmd file", odt_document())
rmarkdown::render("your rmd file", word_document())
```

or *beamer* (PDF) or *slidy* (HTML) presentation:

```{r, eval=F}
rmarkdown::render("your rmd file", beamer_presentation())
rmarkdown::render("your rmd file", slidy_presentation())
```

---

When the document is generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(mtcars)
```

---

You can also embed plots, for example:

```{r, echo=FALSE}
plot(mpg~hp, data=mtcars, main="Mileage per Horsepower")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
